\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems

### 2023-06-02 TilingProjectDraft/tilingProject.tex
added entanglement implementation

\section{Correlation functions in momentum space}
Similar to Greens functions, our formalism also allows calculating \(k-\)space correlation functions \(\chi(\vec q)\) from knowledge of local and nearst-neighbour correlations \(\chi_\text{loc}\) and \(\chi_\text{nn}\). This is seen by Fourier transforming a generic real-space correlation function \(\chi(\vec r)\) corresponding to the operator \(\mathcal{O}\):
\begin{equation}\begin{aligned}
	\chi(\vec r) = \left<\mathcal{O}_1 (\vec R + \vec r) \mathcal{O}_2(\vec R)\right> = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right>
\end{aligned}\end{equation}
Since the response should not depend on \(\vec R\) (owing to translation invariance), we have
\begin{equation}\begin{aligned}
	\chi(\vec r) = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\delta_{\vec k + \vec q, 0}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right> = \frac{1}{N}\sum_{\vec k} e^{-i \vec k \cdot \vec r}\left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right>
\end{aligned}\end{equation}
By inverting the Fourier transform, we therefore get
\begin{equation}\begin{aligned}
	\chi(\vec k) &\equiv \left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}} \chi(\vec r) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} + \Xi_{\vec k}\chi_\text{nnn}~,
\end{aligned}\end{equation}
where \(\chi_\text{loc},\chi_\text{nn},\chi_\text{nnn}\) are local, nearest-neighbour and next-nearest-neighbour correlation functions, with dispersions \(\xi_{\vec k} = 2\left[\cos(k_x a) + \cos\left(k_y a\right)\right] \) and \(\Xi_{\vec k} = 2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right] \). Following eqs.~\ref{local_correlation} through \ref{nnn_correlation}, these can be cast into impurity model correlation functions:
\begin{equation}\begin{aligned}
	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right] 
\end{aligned}\end{equation}

@@

The density matrix of the full Hamiltonian in ground-state is simply \(\rho = \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\). In order to calculate entanglement measures in and among \(k-\)space states, we begin by obtaining an expression for the von-Neumann entropy of a \(\vec k-\)state, in terms of auxiliary model computables. The reduced density matrix for the momentum state involves a partial trace over its configurations:
	\rho_{\vec k,\sigma} = \sum_{n_{\vec k,\sigma}=0,1}\braket{n_{k,\sigma} | \Psi_\text{gs}}\braket{\Psi_\text{gs} | n_{\vec k,\sigma}} = \sum_{n_{\vec k,\sigma}=0,1}|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2
where \(\ket{n_{\vec k,\sigma}}\) represents a state in Fock space with \(n_{\vec k,\sigma}\) number of particles in the single particle state with momentum \(\vec k\) and spin \(\sigma\). We now Fourier transform the overlap and retain terms up to the next-nearest neighbour:
	|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq \braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0,\sigma} | \Psi_\text{gs}} + \xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}} + \Xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a^\prime,\sigma} | \Psi_\text{gs}}
where \(\vec a\) and \(\vec a^\prime\) are nearest and next-nearest neighbour sites to \(\vec R_0\), and \(\xi_{\vec k}\) and \(\Xi_{\vec k}\) have been defined above. Following the eqs.~\ref{local_correlation} through \ref{nnn_correlation}, we can identify \(\hat O_1^\dagger(\vec R) = \hat O_2(\vec R) = \ket{n_{\vec R_0,\sigma}}\bra{n_{\vec R,\sigma}}\), so that we have, for example, \(\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}} = \braket{\hat O_1(\vec R_0) \hat O_2(\vec R_0 + \vec a)}\). The, using eqs.~\ref{local_correlation} through \ref{nnn_correlation}, the Fourier transform becomes:
	|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux} | n_{d,\sigma}}\braket{n_{d,\sigma} | \psi_\text{aux}} + \frac{1}{\mathcal{W}}\braket{\psi_\text{aux} | n_{z,\sigma}}\braket{n_{z,\sigma} | \psi_\text{aux}}\right]\\
							      &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{z,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{d,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{z,\sigma}}\right) \psi_\text{aux}}\right] \\
		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{d,\sigma}}\right) \psi_\text{aux}}\right]
The \(k-\)space reduced density matrix takes the form
	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{d\sigma}} + \frac{1}{\mathcal{W}}\bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{z\sigma}}\right]\\
							      &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{1\sigma}}\right] \\
		    &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{1\sigma}}\right]
where \(\bar\psi_{n_{d\sigma}} = \braket{n_{d,\sigma} | \psi_\text{aux}}\) and similar definitions exist for \(\alpha_{n_{z\sigma}}\) and \(\alpha_{n_{1\sigma}}\). The von-Neumann entropy \(S_\text{EE}(\vec k)\) can then be calculated by taking the trace of the operator \(\rho_{\vec k,\sigma}\ln \rho_{\vec k,\sigma}\).

\section{The Mott MIT: a local perspective}
\subsection{Gapping of the local spectral function and vanishing of correlations}
At a critical value \(U_b = -J/4\) of the local correlation \(U_b\) on the bath zeroth site, the couplings \(J\) and \(V\) of the auxiliary model become irrelevant while \(U\) becomes remains non-zero, leading to a low-energy phase where the impurity is cutt off from the conduction bath. This is the local moment phase, where low-energy excitations have been gapped out.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.48\textwidth]{phase-map-MIT.pdf}
	\includegraphics[width=0.48\textwidth]{spectral-function_dd.pdf}
	\caption{{\it Left:} Phase diagram of the extended SIAM auxiliary model. As the parameter \(r\) is tuned through 0.25, the metallic blue phase changes into the insulating violet phase. {\it Right:} Local spectral function of the auxiliary model. It shows a hard gap for \(r/r_c > 1\).}
	\label{spec_func_mit}
\end{figure}

>>>>

\section{Correlation functions in momentum space}
Similar to Greens functions, our formalism also allows calculating \(k-\)space correlation functions \(\chi(\vec q)\) from knowledge of local and nearst-neighbour correlations \(\chi_\text{loc}\) and \(\chi_\text{nn}\). This is seen by Fourier transforming a generic real-space correlation function \(\chi(\vec r)\) corresponding to the operator \(\mathcal{O}\):
\begin{equation}\begin{aligned}
	\chi(\vec r) = \left<\mathcal{O}_1 (\vec R + \vec r) \mathcal{O}_2(\vec R)\right> = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right>
\end{aligned}\end{equation}
Since the response should not depend on \(\vec R\) (owing to translation invariance), we have
\begin{equation}\begin{aligned}
	\chi(\vec r) = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\delta_{\vec k + \vec q, 0}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right> = \frac{1}{N}\sum_{\vec k} e^{-i \vec k \cdot \vec r}\left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right>
\end{aligned}\end{equation}
By inverting the Fourier transform, we therefore get
\begin{equation}\begin{aligned}
	\chi(\vec k) &\equiv \left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}} \chi(\vec r) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} + \Xi_{\vec k}\chi_\text{nnn}~,
\end{aligned}\end{equation}
where \(\chi_\text{loc},\chi_\text{nn},\chi_\text{nnn}\) are local, nearest-neighbour and next-nearest-neighbour correlation functions, with dispersions \(\xi_{\vec k} = 2\left[\cos(k_x a) + \cos\left(k_y a\right)\right] \) and \(\Xi_{\vec k} = 2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right] \). Following eqs.~\ref{local_correlation} through \ref{nnn_correlation}, these can be cast into impurity model correlation functions:
\begin{equation}\begin{aligned}
	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right] 
\end{aligned}\end{equation}

@@

\begin{itemize}
	\item \(n_{\vec R_0}\rho n_{\vec R_0}\) + \(n_{\vec R_0 + \vec a}\rho n_{\vec R_0 + \vec a}\)
	\item \(e^{i \vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\rho n_{\vec R_0}\) + h.c. + 
	      \(e^{-i \vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\rho n_{\vec R_0}\) + h.c.
	\item \(c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0 + \vec a}\rho n_{\vec R_0}\) + h.c.
	\item   \(e^{2i\vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c. + 
		\(c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c.
	\item \(e^{i \vec{q}\cdot\vec{a}} n_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c. + \(e^{-i \vec{q}\cdot\vec{a}} n_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\) + h.c.
\end{itemize}
\subsection{\(k-\)space von-Neumann entropy}
The density matrix of the full Hamiltonian in ground-state is simply \(\rho_\text{gs} = \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\). In order to calculate entanglement measures in and among \(k-\)space states, we begin by obtaining an expression for the von-Neumann entropy of a \(\vec k-\)state, in terms of auxiliary model quantities. 
The full ground state \(\ket{\Psi_\text{gs}}\) can be written in the basis of the Fock states of momentum \(\vec k\sigma\):
\begin{equation}\begin{aligned}
	\Psi_\text{gs} = \sin\theta_{\vec k\sigma} \ket{n_{\vec k\sigma} = 0}\otimes\ket{\phi_{\vec k\sigma}} + \cos\theta_{\vec k\sigma} \ket{n_{\vec k\sigma} = 1}\otimes\ket{\bar\phi_{\vec k\sigma}}
\end{aligned}\end{equation}
where \(\ket{n_{\vec k\sigma}}\) is the state with occupancy \(n_{\vec k\sigma}\) from the Hilbert space of \(\vec k\sigma\). \(\ket{\phi_{\vec k\sigma}}\) and \(\ket{\bar\phi_{\vec k\sigma}}\) are the normalised states representing the configuration of the remaining degrees of freedom in the full state \(\Psi_\text{gs}\) when \(\hat n_{k\sigma}\) is 0 and 1 respectively. \(\sin \theta_{\vec k}\) and \(\cos\theta_{\vec k\sigma}\) are the probabilities of obtaining \(n_{\vec k\sigma}\) to be 0 and 1 respectively, in the full ground state.

The reduced density matrix for the momentum state \(\vec k\sigma\) is then obtained simply by tracing over the states \(\ket{n_{\vec k\sigma}}\):
\begin{equation}\begin{aligned}
	\rho_{\vec k\sigma} = \sum_{n_{\vec k\sigma}=0,1} \braket{n_{\vec k\sigma} | \rho_\text{gs} | n_{\vec k\sigma}} = \sin^2\theta_{\vec k\sigma} \ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}} + \cos^2\theta_{\vec k\sigma} \ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}\label{red_matrix}
\end{aligned}\end{equation}
If the eigenvalues of the operators \(\ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}}\) and \(\ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}\) are \(\left\{ \lambda_n \right\} \) and \(\left\{ \bar\lambda_n \right\} \) respectively, the von-Neumann entropy is given by
\begin{equation}\begin{aligned}
	S_\text{EE}\left(\rho_{\vec k\sigma}\right) = \sum_n \left( \sin^2\theta_{\vec k\sigma}\lambda_n + \cos^2\theta_{\vec k\sigma}\bar\lambda_n \right) 
\end{aligned}\end{equation}

In order to connect with the auxiliary model, we will need to obtain the reduced density matrix without tracing out any states. We will, instead, project on to the appropriate states with the particle number operator \(\hat n_{\vec k\sigma}\) and the hole number operator \(\hat h_{\vec k\sigma} = 1 - \hat n_{\vec k\sigma}\). The reduced density matrix can be obtained by applying such projectors:
\begin{equation}\begin{aligned}
	\rho_{\vec k\sigma} \equiv \hat n_{\vec k\sigma}\rho_\text{gs} \hat n_{\vec k\sigma} + \hat h_{\vec k\sigma}\rho_\text{gs} \hat h_{\vec k\sigma} = \sin^2\theta_{\vec k\sigma} \ket{0}\bra{0}\otimes\ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}} + \cos^2\theta_{\vec k\sigma} \ket{1}\bra{1}\otimes\ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}\label{red_matrix_projection}
\end{aligned}\end{equation}
where \(\ket{1}\) and \(\ket{0}\) are the \(n_{\vec k\sigma}=1\) and 0 states respectively. In the basis \(\left\{ \ket{0}, \ket{1} \right\} \), the reduced density matrix can be represented as
\begin{equation}\begin{aligned}
	\rho_{\vec k\sigma} = \begin{pmatrix}\sin^2\theta_{\vec k\sigma} \ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}} & 0 \\ \\
	0 & \cos^2\theta_{\vec k\sigma} \ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}
	\end{pmatrix} ~,
\end{aligned}\end{equation}
such that the eigenvalues of this matrix are the same as those of the operator in eq.~\ref{red_matrix}; the projection method would therefore give the same von-Neumann entropy as that obtained using the partial traces.

We will now Fourier transform the reduced matrix from the definition in eq.~\ref{red_matrix_projection}, and retain terms up to the nearest neighbour, by expanding \(c_{\vec k\sigma}\) as \(c_{\vec R_0,\sigma} + \xi_{\vec k}c_{\vec R_0 + \vec a,\sigma}\), where \(\vec a\) is the nearest neighbour site to \(\vec R_0\), and \(\xi_{\vec k}\) has been defined above.
\begin{equation}\begin{aligned}
	\hat n_{\vec k\sigma}\ket{\Psi_\text{gs}} \to  \left[ \hat n_{\vec R_0,\sigma} + \sum_{\vec a} \hat n_{\vec R_0 + \vec a,\sigma} + \sum_{\vec a}\left( e^{i \vec{k}\cdot\vec{a}}c^\dagger_{\vec R_0,\sigma}c_{\vec R_0 + \vec a,\sigma} + \text{h.c.} \right) \right]\ket{\Psi_\text{gs}}
\end{aligned}\end{equation}
We also expand the ground state wavefunction: \(\ket{\Psi}_\text{gs} \simeq \ket{\psi_\text{aux}} = \frac{1}{\sqrt \mathcal{W}}\sum_{\vec a \in \text{NN of }\vec R_0}\ket{\psi_\text{aux}(\vec R_0,\vec a)}\), so that we get
\begin{equation}\begin{aligned}
	\hat n_{\vec k\sigma}\ket{\Psi_\text{gs}} &= \frac{1}{\sqrt \mathcal{W}}\left[ \hat n_{\vec R_0,\sigma} \sum_{\vec a}\ket{\psi_\text{aux}(\vec R_0,\vec a)} + \sum_{\vec a} \hat n_{\vec R_0 + \vec a,\sigma}\ket{\psi_\text{aux}(\vec R_0,\vec a)} + \sum_{\vec a}\left( e^{i \vec{k}\cdot\vec{a}}c^\dagger_{\vec R_0,\sigma}c_{\vec R_0 + \vec a,\sigma} + \text{h.c.} \right) \ket{\psi_\text{aux}(\vec R_0,\vec a)}\right]\\
						  &=\hat n_{d,\sigma} \ket{\psi_\text{aux}} + \hat n_{z,\sigma}\ket{\psi_\text{aux}} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right) \ket{\psi_\text{aux}}
\end{aligned}\end{equation}
By taking the outer product with its hermitian conjugate, we get the reduced density matrix:
\begin{equation}\begin{aligned}
	\rho_{\vec k\sigma} \simeq \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_\text{aux} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\label{density_matrix_kspace}
\end{aligned}\end{equation}
The von-Neumann entropy \(S_\text{EE}(\vec k)\) can then be calculated by taking the trace of the operator \(\rho_{\vec k\sigma}\ln \rho_{\vec k\sigma}\).

\subsection{\(k-\)space mutual information}
Another measure of many-body correlations would be the mutual information between two momentum-space states. The mutual information \(I_2\) between the states \(\ket{\vec k, \sigma}\) and \(\ket{-\vec k, \sigma}\) is defined as
\begin{equation}\begin{aligned}
	I_2(\vec k\sigma:-\vec k\sigma) = S_\text{EE}(\rho_{\vec k\sigma}) + S_\text{EE}(\rho_{-\vec k\sigma}) - S_\text{EE}(\rho_{\vec k\sigma, -\vec k\sigma})~,
\end{aligned}\end{equation}
where \(S_\text{EE}(\rho)\) is the von-Neumann entropy associated with the density matrix \(\rho\). The reduced density matrices \(\rho_{\pm\vec k\sigma}\) can be computed using eq.~\ref{density_matrix_kspace}; the reduced density matrix \(\rho_{\vec k\sigma, \vec k\sigma}\) has both the states \(\pm \vec k\) traced out, and it can be obtained by substituting \(\rho_{\vec k\sigma}\) back into eq.~\ref{density_matrix_kspace}:
\begin{equation}\begin{aligned}
	\rho_{\vec k\sigma, -\vec k\sigma} &= \hat n_{-\vec k\sigma}\rho_{\vec k\sigma}\hat n_{-\vec k\sigma} + \hat h_{-\vec k\sigma}\rho_{\vec k\sigma}\hat h_{-\vec k\sigma} \\
					   &= \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{-\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{-\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]
\end{aligned}\end{equation}

\section{The Mott MIT: a local perspective}
\subsection{Gapping of the local spectral function and vanishing of correlations}
At a critical value \(U_b = -J/4\) of the local correlation \(U_b\) on the bath zeroth site, the couplings \(J\) and \(V\) of the auxiliary model become irrelevant while \(U\) becomes remains non-zero, leading to a low-energy phase where the impurity is cut off from the conduction bath. This is the local moment phase, where low-energy excitations have been gapped out.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.48\textwidth]{phase-map-MIT.pdf}
	\includegraphics[width=0.48\textwidth]{spectral-function_dd.pdf}
	\caption{{\it Left:} Phase diagram of the extended SIAM auxiliary model. As the parameter \(r\) is tuned through 0.25, the metallic blue phase changes into the insulating violet phase. {\it Right:} Local spectral function of the auxiliary model. It shows a hard gap for \(r/r_c > 1\).}
	\label{spec_func_mit}
\end{figure}
